О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Add one more citation

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ (and every characteristic $q$~--- see~\cite{kurz2005characteristic} for details)
there exists a facher set $M\in\mathfrak{M}(2,n)$ (with the desired characteristic).

>>>>

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ (and every characteristic $q$~--- see~\cite{kurz2005characteristic} for details)
there exists a facher set $M\in\mathfrak{M}(2,n)$ (with the desired characteristic~\cite[Theorem 5]{our-vmmsh-2018}).
